---
title: "Analysis of Used Cars Dataset"
author: "Farooq A. Khan"
date: "30/07/2020"
output:
  html_document:
    toc: true
    toc_float: true
---

## The dataset
There are 13 cars datasets that have been defined below: 

```{r}
companies<-c('audi', 'bmw', 'cclass', 'focus', 'ford', 'hyundi', 'merc', 'skoda', 'toyota', 'unclean cclass', 'unclean focus', 'vauxhall', 'vw')
```


## Analyze Toyota
```{r}
toyota <- read.csv('../data/toyota.csv')
```

Here is the dataset: 
```{r}
library(knitr)
kable(toyota[1:5,], caption="First Five Rows of Toyota dataset")
```

Here are some unique models of Toyota cars: 
```{r}
kable(unique(toyota[,'model']), caption="Unique models of Toyota Cars")
```

Here is also unique fuel types. 
```{r}
kable(unique(toyota[,'fuelType']), caption="Unique fuel types of Toyota Cars")
```


### Graphical Analysis
Below we graph the mileage to price scatter plot and group the cars based on Fuel Type. As you can see the cheapest cars are those with "Petrol" as a fuel Type. 
```{r}
library(ggplot2)
ggplot(toyota, aes(mileage, price, colour=fuelType)) + 
  geom_point()
```
We can also look at which cars are expensive based on their model as well. Below is a graph that shows that C-HR are cheapest models while the Proace Verso are more expensive on average. 
```{r}
ggplot(toyota, aes(mileage, price, colour=model)) + geom_point()
```

Below you can see that there are alot of toyota cars that run on petrol. 
```{r}
ggplot(toyota) + geom_bar(aes(x=fuelType))
```

The two most common types of cars are Aygo and Yaris.
```{r}
ggplot(toyota) + geom_bar(aes(x=model))
```

Lets compare engine size to price. Small engine sizes yield cheaper prices with higher mileage. 
```{r}
ggplot(toyota, aes(mileage, price, colour=engineSize)) + geom_point()
```

```{r}
ggplot(toyota, aes(tax, price, colour=fuelType)) + geom_point()
```
Tax appears to be a finite set of values and not a part of the real plane. Also the hypothese is that cars that are not eco friendly will be taxed more. 

```{r}
ggplot(toyota, aes(year, price, colour=fuelType)) + geom_point()
```

## Linear COrrelation
```{r}
cor(toyota$mileage, toyota$price)
```
There is negative weak correlation between mileage and price. 
```{r}
cor(toyota$tax, toyota$price)
```
There is also weak correlation between tax and price. 


## Forming Linear Models

```{r}
model <- lm(formula=price ~ year + mileage + tax + mpg + engineSize, data=toyota)
summary(model)
```
The R-suqred and adjusted R-squared value is 0.764 showing positive moderate correlation.

Lets try it wihtout tax this time and see the R-squared value. 
```{r}
model2<- lm(formula=price ~ year + mileage + mpg + engineSize, data=toyota)
summary(model2)
```
Computationally better but mathematically the same. 
